SPIN Novelty

### 2019-04-10 stats/kids_basic_me.Rmd
update combination experiment

@@

>>>>

## Facets by item

ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")
```

@@

```{r plot by numerical age, echo = F}
p4 <- d %>%
  filter(trial != "train1",
         trial != "train2")%>%
    group_by(subage,age_num,subid,subage)%>%
  multi_boot_standard(col = "correct")

ggplot(data = p4, aes(x = age_num, y = mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_smooth(method = "lm", se = T, alpha = .5)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")
```

### 2019-04-10 stats/kids_novelty.Rmd
update combination experiment

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  select(-pick_src)

@@

d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         leftObject = leftFruit,
         rightObject = rightFruit, 
         pick = str_sub(pick,72,str_length(pick)-4),
         condition = "dis_novelty_mcc")%>%
  filter(speakerChange == "false", trial != "train")%>%
  select(-speakerChange,-altAgent,-leftFruit,-rightFruit)

@@

## sanity checks
d %>%
  group_by(condition,subage) %>%
  summarise(n = length(unique(subid)))

@@

```{r}
p1 <- d %>%
  group_by(condition,subage, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_point(data = p1, aes(x = subage, y = correct, col = condition, alpha = .2), position = position_jitterdodge(dodge.width = .6, jitter.width = .2, jitter.height = .05))+
  geom_pointrange(data = p2, aes(x = subage, y = mean, col = condition, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()

@@

```{r plot by numerical age}
p5 <- d %>%
  group_by(condition,age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = condition)) +
  geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

@@

# maximal converging model
bm <- brm(correct ~ age_num * condition + (1 | subid) + (age_num * condition | agent), 
          data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

>>>>

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  select(-pick_src)

@@

d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         leftObject = leftFruit,
         rightObject = rightFruit, 
         pick = str_sub(pick,72,str_length(pick)-4),
         experiment = "dis_novelty_mcc")%>%
  filter(speakerChange == "false", trial != "train")%>%
  select(-speakerChange,-altAgent,-leftFruit,-rightFruit)

@@

## sanity checks
d %>%
  group_by(experiment,subage) %>%
  summarise(n = length(unique(subid)))

@@

```{r}
p1 <- d %>%
  group_by(experiment,subage, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_point(data = p1, aes(x = subage, y = correct, col = experiment, alpha = .2), position = position_jitterdodge(dodge.width = .6, jitter.width = .2, jitter.height = .05))+
  geom_pointrange(data = p2, aes(x = subage, y = mean, col = experiment, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = .5))+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()

@@

```{r plot by numerical age}
p5 <- d %>%
  group_by(experiment,age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct, col = experiment)) +
  geom_smooth(data = d, aes(x = age_num, y = correct),method = "glm", method.args = list(family = "binomial"), se = T, alpha = .3)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

@@

# maximal converging model
bm <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
          data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)
